BOLD Parameter Estimation Using Particle Filters

### 2010-06-30 doc/thesis/methods.tex
conclusion in background
work on particle filter.

\chapter{Methods}
This paper describes two types of experiments; first we will cover
simulations, which of course have the benefit of a ground truth, second
we will cover the methods for real data.

>>>>

\chapter{Methods}
\section{Prior Distribution}
For the BOLD signal all the parameters have been studied and have relatively well
known mean and variance, so a prior is helpful. 
For strictly positive parameters (members of $x$) we used a gamma distribution,
whereas for parameters that could be negative, we used a Gaussian distribution. In
both cases standard deviations twice that found in previous studies were used.
